### 2019-08-10 README.Rmd
added thought to readme

- Can I remove some of the sources from the references file that I am not going to use?

>>>>

- I am thinking about moving the paper to a new repository and then renaming this repository as LIME-research-journals and using it more as a place to try stuff out
- Can I remove some of the sources from the references file that I am not going to use?
